Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-17 paper/02_noisyRMD.tex
section 2 proof read; iterated diffusion analysis

Fix a signaling game with finite states $\States$, messages $\Messgs$
and acts $\Acts$. Let $\Pr(\cdot) \in \Delta{\States}$ be the prior
distribution over states and $\Util_{\sen,\rec} \mycolon \States
\times \Messgs \times \Acts \rightarrow \mathds{R}$ the senders's and
receiver's utility functions. The sender's behavioral strategies are
functions $\Sstrat \in \Delta(\Messgs)^\States$; the receiver's are
functions $\Rstrat \in \Delta(\Acts)^\Messgs$. Define the expected
utility of actions in each choice point are as usual:
\begin{align*}
  \EU(\messg \myts ; \myts \state, \Rstrat) & = \sum_{\act \in \Acts}
  \Rstrat(\act \probbar \messg) \cdot U_\sen(\state, \messg, \act) \\
  \EU(\act \myts ; \myts \messg, \Sstrat) & = \sum_{\state \in
    \States} \Pr(\state) \cdot \Sstrat(\messg \probbar \state) \cdot
  U_\rec(\state, \messg, \act) \,.
\end{align*}
The \emph{fitness} of a behavioral strategy at a choice point is the
frequency-weighted average of expected utilities of each choice, given
the opponent's strategy:
\begin{align*}
  \Phi(\state,\Sstrat, \Rstrat) & = \sum_{\messg} \Sstrat(\messg \probbar \state) \cdot
\EU(\messg \myts ; \myts\state,\Rstrat) \\
\Phi(\messg,\Sstrat, \Rstrat) & = \sum_{\act} \Rstrat(\act \probbar \messg)
\cdot \EU(\act \myts ; \myts \messg,\Sstrat)\,.
\end{align*}
The discrete-time replicator dynamic maps current strategies $\Sstrat$
and $\Rstrat$ to future strategies $\RD(\Sstrat)$ and $\RD(\Rstrat)$ in
such a way that changes in frequency are proportional to expected
utilities. For behavioral strategies, the changes take place locally
at each of the agents' choice points:\todo{could be shortened by using
  $\propto$ notation}
\begin{align*}
  \RD(\Sstrat)(\messg \probbar \state) & = \frac{\Sstrat(\messg \probbar \state) \cdot
    \EU(\messg \myts ; \myts \state,\Rstrat)} {\Phi(\state,\Sstrat, \Rstrat)} \\
    \RD(\Rstrat)(\act \probbar \messg) & = \frac{\Rstrat(\act \probbar \messg) \cdot
    \EU(\act \myts ; \myts \messg,\Sstrat)} {\Phi(\messg,\Sstrat, \Rstrat)}  \,.
\end{align*}

\todo[inline]{example? sim-max game 10 states, after so and so many rounds?}

@@

The aggregate effect of confusion of states on behavioral strategies
can be captured in a function that maps behavioral strategies
$\Sstrat$ and $\Rstrat$ to their noise-perturbed realizations
$C(\Sstrat)$ and $C(\Rstrat)$. The idea is that $\Sstrat$ and
$\Rstrat$ are what, on average, the idealized, confusion-free behavior
would be, while $C(\Sstrat)$ and $C(\Rstrat)$ are behavioral
strategies that describe the agents' actual noise-perturbed
probabilistic behavior. If we conceive of behavioral strategies
$\Sstrat$ and $\Rstrat$ as row-stochastic matrices, the effect of
state confusability is easily captured by matrix multiplication as:
\begin{align*}
  C(\Sstrat) & = C \Sstrat &    C(\Rstrat) & = \Rstrat C\,.
\end{align*}

The discrete-time replicator diffusion dynamic takes the replicator
dynamic as basic, but factors in the confusion of states at each
update step in a sequential update:
\begin{align*}
  \RDD(\Sstrat) & = C(\RD(\Sstrat)) &   \RDD(\Rstrat) & = C(\RD(\Rstrat)) \,.
\end{align*}
This is equivalent to the following, perhaps more transparent
formulation, given by \citet{Correia2013:The-Bivalent-Tr}:
\begin{align*}
  \RDD(\Sstrat)(\messg \probbar \state_i) & = \sum_{j} C_{ij} \cdot
  \frac{\Sstrat(\messg \probbar \state_j) \cdot
    \EU(\messg \myts ; \myts \state_j,\Rstrat)}
  {\Phi(\state_j,\Sstrat, \Rstrat)} \\
    \RDD(\Rstrat)(\state_i \probbar \messg) & = \sum_{j} C_{ij} \cdot
  \frac{\Rstrat(\state_j \probbar \messg) \cdot
    \EU(\state_j \myts ; \myts \messg,\Sstrat)} {\Phi(\messg,\Sstrat, \Rstrat)}  \,.
\end{align*}

@@

The replicator mutator dynamic (\rmd) has been proposed by Martin
Nowak first in the context of signaling game models for the evolution
of grammar
\citep[e.g.][]{KomarovaNiyogi2001:The-Evolutionar,NowakKomarova2001:Evolution-of-Un,Nowak2006:Evolutionary-Dy}. The
relation of the \rmd to other prominent evolutionary dynamics is well
understood \citep{PageNowak2002:Unifying-Evolut}. The \rmd has seen
further fruitful applications in the context of signaling games
\citep[e.g.][]{HutteggerSkyrms2010:Evolutionary-Dy,Deo2014:The-Semantic-an}. It
is therefore desirable to relate the \rdd that we propose here to the
\rmd.

@@

For mixed strategies, we define the players' fitness in the
usual manner. Let $F_i^{\Rmixed}$ be $\Spure_i$'s fitness given
$\Rmixed$ and $F_i^{\Smixed}$ be $\Rpure_i$'s fitness given
$\Smixed$. Then $\Phi(\Smixed,\Rmixed) = \sum_{k} \Smixed_k \cdot
F_k^{\Rmixed}$ is the average fitness in the sender population and
$\Phi(\Rmixed,\Smixed) = \sum_{k} \Rmixed_k \cdot F_k^{\Smixed}$ the
average fitness in the receiver population.\todo{give actual
  definition of fitness etc.?}

The continuous-time replicator dynamic defines the change of frequency
of mixed strategies. Its so-called two-population version that takes
sender and receiver roles into account separately is defined as:
\begin{align*}
  \dot{\Smixed_i} & = \Smixed_i \cdot \left ( F_i^{\Rmixed} -
  \Phi(\Smixed,\Rmixed) \right ) &   \dot{\Rmixed_i} &  = \Rmixed_i \cdot \left ( F_i^{\Smixed} -
  \Phi(\Rmixed,\Smixed) \right ) \,.
\end{align*}
Similar to the version for behavioral strategies, a discrete-time
version of the \rd for mixed strategies can be conceptualized as an
update function that maps mixed strategies $\Smixed$ and $\Rmixed$
onto mixed strategies $\RD(\Smixed)$ and $\RD(\Rmixed)$ respectively,
such that:
\begin{align*}
  \RD(\Smixed)_i & = \frac{\Smixed_i \cdot F_i^{\Rmixed}}{
    \Phi(\Smixed,\Rmixed)} & \RD(\Rmixed)_i & = \frac{\Rmixed_i \cdot
    F_i^{\Smixed}}{ \Phi(\Rmixed,\Smixed)} \,.
\end{align*}

@@

\begin{proof}
  It suffices to check either sender or receiver part. Focusing on the
  former, we need to show that the continuous version is derivable
  from the discrete version if the discrete update steps get
  infinitely small so that:
  \begin{align*}
    \dot{\Smixed_i} & = \Smixed_i' - \Smixed_i = \sum_{j} Q_{ji}
    \frac{\Smixed_j \cdot F_j^{\Rmixed}}{ \Phi(\Smixed,\Rmixed)} -
    \Smixed_i = \sum_{j} \Smixed_j \left ( \frac{ Q_{ji} \cdot
        F_j^{\Rmixed}}{ \Phi(\Smixed,\Rmixed)} - \Smixed_i \right ) \\
    & = \sum_{j} \Smixed_j \left ( \frac{ Q_{ji} \cdot
        F_j^{\Rmixed} - \Smixed_i \cdot \Phi(\Smixed,\Rmixed)}{ \Phi(\Smixed,\Rmixed)}  \right )
  \end{align*}
  As $\Phi(\Smixed,\Rmixed)$ is a constant rate of change, we can drop
  it to derive the non-payoff adjusted continuous version above,
  since:
  \begin{align*}
    & \sum_{j} \Smixed_j \left ( Q_{ji} \cdot
        F_j^{\Rmixed} - \Smixed_i \cdot \Phi(\Smixed,\Rmixed)  \right
      ) =     \sum_{j} \Smixed_j  Q_{ji} \cdot
        F_j^{\Rmixed} - \sum_{j} \Smixed_j \cdot \Smixed_i \cdot
        \Phi(\Smixed,\Rmixed) \\
       = &    \sum_{j} \Smixed_j  Q_{ji} \cdot
        F_j^{\Rmixed} - \Smixed_i \cdot
        \Phi(\Smixed,\Rmixed) 
  \end{align*}
\end{proof}

@@

The sequential reformulation of the \rmd in terms of a sequence of
updates already closely resembles our initial formulation of the
\rdd. However, there is a major difference between these. While the
\rdd is a dynamic for behavioral strategies, the \rmd, as taken from
the literature, is a dynamic for mixed strategies. Similarly, the
confusability of states is an operation that is straightforwardly
definable for behavioral strategies (see Equation~XYZ), while mutation
in the \rmd is defined as mutation from one pure strategy to
another. Nonetheless, it is possible to map each confusion matrix to a
mutation matrix in such a way that the natural correspondence between
strategies is conserved (see
Figure~\ref{fig:correspondence-result}). This is the main result
presented in this section, and it is our justification for regarding
the \rdd as the behavioral-strategy analogue of the replicator-mutator
dynamic when the only source of mutation is perceptual confusion of
states.

@@

More concretely, since there is a non-injective mapping $G$ from
behavioral to mixed strategies, we would like to show that there is a
systematic translation from a confusion matrix $C$ to a mutation
matrices $Q^C$ such that for each mixed sender strategy $\Smixed$, its
unique corresponding behavioral strategy $\Sstrat = G(\Smixed)$ has a
confusion-perturbation $C(\Sstrat)$ that corresponds, via $G$ to the
mutation-perturbation $Q^C(\Smixed)$ (see
Figure~\ref{fig:correspondence-result}). In other words, we
hypothesize that a confusion matrix $C$ should give rise to a unique
mutation matrix $Q^C$ so that whenever $G(\Smixed) = \Sstrat$ we also
have $G(Q^C(\Smixed)) = C(\Sstrat)$. Similarly, for the receiver. This
is the content of Theorems~\ref{thm:sender-eq} and
~\ref{thm:receiver-eq}), the proofs of which are in
Appendix~\ref{sec:proofs}. The remainder of this section introduces
the relevant construction that maps arbitrary $C$ to suitable $Q^C$.

@@

The probability that $\Rpure_i$ mutates into $\Rpure_j$ is the product of
the probabilities for each $\messg$ that the state $\Rpure_i(\messg)$ is
perceived as state $\Rpure_j(\messg)$. Abusing notation, by referring to
the indices of states $\Rpure_i(\messg)$ and $\Rpure_j(\messg)$ with
$\Rpure_i(\messg)$ and $\Rpure_j(\messg)$ directly, we define:
\begin{align}
  \label{eq:construction-rec}
  R^C_{ij} = \prod_{\messg} C_{\Rpure(\messg)\Rpure'(\messg)}\,.
\end{align}

>>>>

Fix a signaling game with finite states $\States$, messages $\Messgs$
and acts $\Acts$. Let $\Pr(\cdot) \in \Delta{\States}$ be the prior
distribution over states and $\Util_{\sen,\rec} \mycolon \States
\times \Messgs \times \Acts \rightarrow \mathds{R}$ the senders's and
receiver's utility functions. The sender's behavioral strategies are
functions $\Sstrat \in \Delta(\Messgs)^\States$; the receiver's are
functions $\Rstrat \in \Delta(\Acts)^\Messgs$. Define the expected
utility of actions in each choice point are as usual:
\begin{align*}
  \EU(\messg \myts ; \myts \state, \Rstrat) & = \sum_{\act \in \Acts}
  \Rstrat(\act \probbar \messg) \cdot U_\sen(\state, \messg, \act) \\
  \EU(\act \myts ; \myts \messg, \Sstrat) & = \sum_{\state \in
    \States} \Pr(\state) \cdot \Sstrat(\messg \probbar \state) \cdot
  U_\rec(\state, \messg, \act) \,.
\end{align*}
The \emph{fitness} of a behavioral strategy at a choice point is the
frequency-weighted average of expected utilities of each choice, given
the opponent's strategy:
\begin{align*}
  \Phi(\state,\Sstrat, \Rstrat) & = \sum_{\messg} \Sstrat(\messg \probbar \state) \cdot
\EU(\messg \myts ; \myts\state,\Rstrat) \\
\Phi(\messg,\Sstrat, \Rstrat) & = \sum_{\act} \Rstrat(\act \probbar \messg)
\cdot \EU(\act \myts ; \myts \messg,\Sstrat)\,.
\end{align*}
The discrete-time replicator dynamic maps current strategies $\Sstrat$
and $\Rstrat$ to future strategies $\RD(\Sstrat)$ and $\RD(\Rstrat)$
in such a way that changes in frequency are proportional to expected
utilities. For behavioral strategies, the changes take place locally
at each of the agents' choice points:
\begin{align*}
  \RD(\Sstrat)(\messg \probbar \state) & = \frac{\Sstrat(\messg \probbar \state) \cdot
    \EU(\messg \myts ; \myts \state,\Rstrat)} {\Phi(\state,\Sstrat, \Rstrat)} \\
    \RD(\Rstrat)(\act \probbar \messg) & = \frac{\Rstrat(\act \probbar \messg) \cdot
    \EU(\act \myts ; \myts \messg,\Sstrat)} {\Phi(\messg,\Sstrat, \Rstrat)}  \,.
\end{align*}

@@

The aggregate effect of confusion of states on behavioral strategies
can be captured in a function that maps behavioral strategies
$\Sstrat$ and $\Rstrat$ to their noise-perturbed realizations
$C(\Sstrat)$ and $C(\Rstrat)$. The idea is that $\Sstrat$ and
$\Rstrat$ are what, on average, the idealized, confusion-free behavior
would be, while $C(\Sstrat)$ and $C(\Rstrat)$ are behavioral
strategies that describe the agents' actual noise-perturbed
probabilistic behavior. If we conceive of behavioral strategies
$\Sstrat$ and $\Rstrat$ as row-stochastic matrices, the effect of
state confusability is easily captured by matrix multiplication as:
\begin{align}
  \label{eq:confusion-function}
  C(\Sstrat) & = C \Sstrat &    C(\Rstrat) & = \Rstrat C\,.
\end{align}

The discrete-time replicator diffusion dynamic takes the replicator
dynamic as basic, but factors in the confusion of states at each
update step in a sequential update:
\begin{align*}
  \RDD(\Sstrat) & = C(\RD(\Sstrat)) &   \RDD(\Rstrat) & = C(\RD(\Rstrat)) \,.
\end{align*}
This is equivalent to the following, perhaps more transparent
formulation, given by \citet{Correia2013:The-Bivalent-Tr}:
\begin{align*}
  \RDD(\Sstrat)(\messg \probbar \state_i) & = \sum_{j} C_{ij} \cdot
  \frac{\Sstrat(\messg \probbar \state_j) \cdot
    \EU(\messg \myts ; \myts \state_j,\Rstrat)}
  {\Phi(\state_j,\Sstrat, \Rstrat)} \\
    \RDD(\Rstrat)(\state_i \probbar \messg) & = \sum_{j} C_{ji} \cdot
  \frac{\Rstrat(\state_j \probbar \messg) \cdot
    \EU(\state_j \myts ; \myts \messg,\Sstrat)} {\Phi(\messg,\Sstrat, \Rstrat)}  \,.
\end{align*}

@@

The replicator mutator dynamic (\rmd) has been proposed first in the
context of signaling game models for the evolution of grammar
\citep[e.g.][]{KomarovaNiyogi2001:The-Evolutionar,NowakKomarova2001:Evolution-of-Un,Nowak2006:Evolutionary-Dy}. The
relation of the \rmd to other prominent evolutionary dynamics is well
understood \citep{PageNowak2002:Unifying-Evolut}. The \rmd has seen
further fruitful applications in the context of signaling games
\citep[e.g.][]{HutteggerSkyrms2010:Evolutionary-Dy,Deo2014:The-Semantic-an}. It
is therefore desirable to relate the \rdd that we propose here to the
\rmd.

@@

Let $F_i^{\Rmixed}$ be $\Spure_i$'s fitness given $\Rmixed$ and
$F_i^{\Smixed}$ be $\Rpure_i$'s fitness given $\Smixed$. Then
$\Phi(\Smixed,\Rmixed) = \sum_{k} \Smixed_k \cdot F_k^{\Rmixed}$ is
the average fitness in the sender population and
$\Phi(\Rmixed,\Smixed) = \sum_{k} \Rmixed_k \cdot F_k^{\Smixed}$ the
average fitness in the receiver population.\todo{give actual
  definition of fitness etc.?}

The continuous-time replicator dynamic defines the change of frequency
of mixed strategies. Its so-called two-population version, that takes
sender and receiver roles into account separately, is defined as:
\begin{align*}
  \dot{\Smixed_i} & = \Smixed_i \cdot \left ( F_i^{\Rmixed} -
  \Phi(\Smixed,\Rmixed) \right ) &   \dot{\Rmixed_i} &  = \Rmixed_i \cdot \left ( F_i^{\Smixed} -
  \Phi(\Rmixed,\Smixed) \right ) \,.
\end{align*}
Similar to the version for behavioral strategies, a discrete-time
version of the \rd for mixed strategies can be conceptualized as an
update function that maps mixed strategies $\Smixed$ and $\Rmixed$
onto mixed strategies $\RD(\Smixed)$ and $\RD(\Rmixed)$ respectively,
such that:
\begin{align*}
  \RD(\Smixed)_i & = \frac{\Smixed_i \cdot F_i^{\Rmixed}}{
    \Phi(\Smixed,\Rmixed)} & \RD(\Rmixed)_i & = \frac{\Rmixed_i \cdot
    F_i^{\Smixed}}{ \Phi(\Rmixed,\Smixed)} \,.
\end{align*}

@@

\begin{proof}
  It suffices to check either sender or receiver part. Focusing on the
  former, we need to show that the continuous version is derivable
  from the discrete version if the discrete update steps get
  infinitely small so that:
  \begin{align*}
    \dot{\Smixed_i} & = \RMD(\Smixed)_i - \Smixed_i = \sum_{j} Q_{ji}
    \frac{\Smixed_j \cdot F_j^{\Rmixed}}{ \Phi(\Smixed,\Rmixed)} -
    \Smixed_i = \sum_{j} \Smixed_j \left ( \frac{ Q_{ji} \cdot
        F_j^{\Rmixed}}{ \Phi(\Smixed,\Rmixed)} - \Smixed_i \right ) \\
    & = \sum_{j} \Smixed_j \left ( \frac{ Q_{ji} \cdot
        F_j^{\Rmixed} - \Smixed_i \cdot \Phi(\Smixed,\Rmixed)}{ \Phi(\Smixed,\Rmixed)}  \right )\,.
  \end{align*}
  As $\Phi(\Smixed,\Rmixed)$ is a constant rate of change, we can drop
  it to derive the non-payoff adjusted continuous version above,
  since:
  \begin{align*}
    & \sum_{j} \Smixed_j \left ( Q_{ji} \cdot
        F_j^{\Rmixed} - \Smixed_i \cdot \Phi(\Smixed,\Rmixed)  \right
      ) =     \sum_{j} \Smixed_j  Q_{ji} \cdot
        F_j^{\Rmixed} - \sum_{j} \Smixed_j \cdot \Smixed_i \cdot
        \Phi(\Smixed,\Rmixed) \\
       = &    \sum_{j} \Smixed_j  Q_{ji} \cdot
        F_j^{\Rmixed} - \Smixed_i \cdot
        \Phi(\Smixed,\Rmixed) 
  \end{align*}
\end{proof}

@@

The sequential reformulation of the \rmd in terms of a sequence of
updates already closely resembles our initial formulation of the
\rdd. However, there is a major difference between these. While the
\rdd is a dynamic for behavioral strategies, the \rmd, as taken from
the literature, applies to mixed strategies. Similarly, the
confusability of states is an operation that is straightforwardly
definable for behavioral strategies (see
Equations~(\ref{eq:confusion-function})), while mutation in the \rmd is
defined as mutation from one pure strategy to another. Nonetheless, it
is possible to map each confusion matrix to a mutation matrix in such
a way that the natural correspondence between strategies is conserved
(see Figure~\ref{fig:correspondence-result}). This is the main result
presented in this section, and it is our justification for regarding
the \rdd as the behavioral-strategy analogue of the replicator-mutator
dynamic when the only source of mutation is perceptual confusion of
states.

@@

More concretely, since there is a non-injective mapping $G$ from
behavioral to mixed strategies, we would like to show that there is a
systematic translation from a confusion matrix $C$ to a mutation
matrices $Q^C$ such that for each mixed sender strategy $\Smixed$, its
unique corresponding behavioral strategy $\Sstrat = G(\Smixed)$ has a
confusion-perturbation $C(\Sstrat)$ that corresponds, via $G$, to the
mutation-perturbation $Q^C(\Smixed)$ (see
Figure~\ref{fig:correspondence-result}). In other words, we
hypothesize that a confusion matrix $C$ should give rise to a unique
mutation matrix $Q^C$ so that whenever $G(\Smixed) = \Sstrat$ we also
have $G(Q^C(\Smixed)) = C(\Sstrat)$. Similarly, for the receiver. This
is the content of Theorems~\ref{thm:sender-eq} and
~\ref{thm:receiver-eq}, the proofs of which are in
Appendix~\ref{sec:proofs}. The remainder of this section introduces
the relevant construction that maps arbitrary $C$ to suitable $Q^C$.

@@

The probability that $\Rpure_i$ mutates into $\Rpure_j$ is the product of
the probabilities for each $\messg$ that the state $\Rpure_i(\messg)$ is
perceived as state $\Rpure_j(\messg)$. Abusing notation by referring to
the indices of states $\Rpure_i(\messg)$ and $\Rpure_j(\messg)$ with
$\Rpure_i(\messg)$ and $\Rpure_j(\messg)$ directly, we define:
\begin{align}
  \label{eq:construction-rec}
  R^C_{ij} = \prod_{\messg} C_{\Rpure_i(\messg)\Rpure_j\messg)}\,.
\end{align}

### 2014-09-17 snippets/iteration_diffusion.Rmd
section 2 proof read; iterated diffusion analysis

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(MCMCpack) # for Dirichlet distribution
source('~/Desktop/data/svn/programming/R/fuzzy-action/dev.r')
```

@@

```{r}
alpha= 0.1
rounds = 10000
ns = 11
nm = 3
states = seq(from=0,to=1,length.out = ns)
C = get.confusion.matrix(states,alpha)
```

@@

But that means that we can define iterated diffusion as either left or right multiplication with suitable powers of the confusion matrix. Therefore define a the n-th power of the confusion matrix.

@@

>>>>

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(MCMCpack) # for Dirichlet distribution
library(ggplot2)
library(reshape2)
# source('~/Desktop/data/svn/programming/R/fuzzy-action/dev.r')
```

@@

```{r}
alpha= 0.1
rounds = 10000
ns = 60
nm = 2
states = seq(from=0,to=1,length.out = ns)

get.confusion.matrix = function(states,alpha){
  ns = length(states)
  if (alpha <= 0){
    return(diag(rep(1,ns)))
  }
  C = matrix(0,nrow=ns, ncol=ns)
  for (i in 1:ns){
    for (j in 1:ns){
      C[i,j] = exp( - (states[i]-states[j])^2 / (alpha^2) )
    }
  }
  return(prop.table(C,1))
}

C = get.confusion.matrix(states,alpha)

@@

We can define iterated diffusion as either left or right multiplication with suitable powers of the confusion matrix. Therefore define a the n-th power of the confusion matrix.

@@

Simple Diffusion
----------------

Let's plot an arbitrary sender and receiver strategy, and apply some noise.

First a function to plot an arbitrary sender and receiver strategy

plotSender = function(sen){
  senDF = melt(sen,varnames = c("state.index","message"), value.name = "probability")
  senDF$states = states[senDF[,1]]
  senDF$message = factor(senDF$message)
  ggplot(senDF, aes(x = states, y=probability, color=message)) + geom_point() + geom_line()
}

sen = rdirichlet(ns,rep(1,nm))

plotSender(sen)
plotSender(get.nbr(sen,C))
plotSender(get.nbr(get.nbr(sen,C),C))

sys.exit()

# rec = rdirichlet(nm,rep(1,ns))
